Evaluation of a Body Photo Browser\footnote{Word Count:2957}

### 2015-04-16 pract3/paper/paper.tex

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{rotating}
\usetikzlibrary{positioning}
\author{Bastiaan Weijers \\ 3256669 \and Colin Smits \\ 4075390}
\title{Evaluation of a Body Photo Browser\footnote{Word Count:2957}}
\renewcommand{\familydefault}{\sfdefault}
\begin{document}
\maketitle
\abstract{A computer vision systems recognising gestures in order to operate a photo browser is reviewed. The system evaluation focuses mainly on the accuracy of the system. We see that some gestures are confused, limiting the system's overall performance. The user evaluation is carried out by usability questionnaires. An overall evaluation is given using the PSSUQ, which shows that the system does not meet the standards set for a computer vision system. Parts of the system are evaluated using ASQ and SEQ, which show difference between tasks within the system. Linking both, we see that the way the system is running short of recognising gestures influences the user's perception of the system. }

@@

\subsection{Methods and Environment}
To quantify the performance of the Body Motion program, we setup a test environment to measure how well the system can translate user interaction to concrete system actions. The test setup is contained in an ecologically sound environment, in this case a bedroom with closed curtains was used with as a primary light source three led bulbs lighting the room. There was a single participant used to create quantifying data, whereas the particular user was well introduced to the workings, capabilities and limitations of the system. An analysis of how the system performs when used by lesser informed participants can be found later on in Section 3 - User Evaluation.
\\ The software was used with a YCrCb spectrum at [..   ...] and a minimum delay of $70ms$ between actions, further settings were left at program-default.
\\ For each action performed in the video recording, a chart was updated with the value the system interpreted it to be. Possible predicted and actual actions were: Next, Previous, CW rotation, CCW rotation and Nothing. Whereas "Nothing" is represented as an idle action wherein nothing happens. It is worth noting that this particular action can only be actively observed on the actual outputs of the system, as predicting idle actions is not possible in our system.
\subsection{Results}
To achieve accurate and representing results, we have recorded a total of 159 actions that we will measure its interpretation by system off, this accounts to roughly 40 actions per possible move.  The number was picked as such because a $n > 30$ will give us a normal distribution over our data [ref needed]. All actions are recorded in a total of two video's, this allows the system to run in a continuous mode, without having to reinitialize after every action. This continuous mode should yield results that are more ecologically sound as opposed to having system global variables reinitialized with every action.
\\ The evaluated output of a the actions will be tested against their expected outputs, the result of this can be found in Table~\ref{table:systemeval}. The data from the table shows the Predicted actions against the Actual actions delivered by the system for every possible action. From the table one can read how many predictions actually translated to correct behavior of the system, and how many did something unexpected.
\\ Table~\ref{table:systemeval} can be parsed to a so-called Confusion Matrix, which is depicted in Table~\ref{table:confusionmatrix}. This matrix is a further generalization and will help us in the question on how well our system performs. Stated before (????, dit is wel in de presentatie gezegd maar nemen we 't op in de paper?), a preferred bias exists in having low false positives as this might be experienced by end-users as undesired behavior. From looking at the Confusion matrix we strongly suspect that we have satisfied this condition, but to confirm this we need to look at the Precision and Recall and establish a PR-curve.
\\ hier een stuk over precision, recall en pr-curve.
\\ moeten we nog een H0 opstellen voor de confusion matrix? We kunnen misschien proeven dat false positive < false negative?
\\ Verder zien we uit Tabel 1 al dat de PR-curve voor swift-left/right er heel anders uit zal zien dan de PR-curve voor rotation. Die laatste is gewoon beroerd, terwijl de precision en recall voor left/right vrij goed zullen zijn. Dit apart testen denk ik in een subhypothese?

@@

\subsection{Methods and Environment}
\label{sub:userMeth}
In our user evaluation, we want to see whether our system is intuitive and easy to use. In order to do that, we need to have a number of people testing our system. First of all, we need to define the environment in which we will be testing. Using the notion of ecological validity, which states that the surroundings in which the research takes place must resemble a real-world setting, the tests will take place in normal rooms in terms of for example lighting and background. A laboratory would not be suitable as the user will react differently. The tests are then carried out as follows.

%Brewer, M. (2000). Research Design and Issues of Validity. In Reis, H. and Judd, C. (eds) Handbook of Research Methods in Social and Personality Psychology. Cambridge:Cambridge University Press.)

@@

Secondly, in order to get measurements, we set up a questionnaire. According to Sauro and Lewis \cite{Quantify}, and Tullis and Albert \cite{Measure}, there are different standardized questionnaires. For our system, we want to know whether the user is satisfied with the system as a whole. As defined by Sauro and Lewis, the PSSUQ (Post-study System Usability Questionnaire) is "designed to access users' perceived satisfaction with computer system applications" \cite{Quantify}. Looking at our goal, we think this questionnaire fits our research. Therefore, we incorporated this questionnaire at the end of the test, after all the scenarios have been completed. We chose the PSSUQ over the SUS (System Usablity Scale), which can also be used as a measure of the usability of a system, due to an increased reliability \cite{Quantify}.

In addition, we thought that the user should be able to tell us what he perceived during each scenario. For that, we set up a combination of the ASQ (After Scenario Questionnaire) and the SEQ (Single Ease Question). The AQS was developed by Lewis in order to describe the user's satisfaction with completing a certain task \cite{Quantify}\cite{ASQ}. This can be perfectly used for our research goal. Moreover, the ASQ is linked to the PSSUQ, and also describes the user's satisfaction with a system, in this case a certain task. Furthermore, as the name suggests, the SEQ is used to describe a user's view on the ease of completing a task. The combination is used to get more reliable results.

@@

From the PSSUQ, we can conclude that the system's performance is not good enough, when compared to the PSSUQ norms \cite{Quantify}.

@@

\thebibliography{99}
\bibitem{Quantify} J. Sauro, J. R. Lewis: \textit{"Quantifying the User Experience"}, Elsevier, 2012
\bibitem{Measure} T. Tullis, W. Albert: \textit{"Measuring the User Experience: Collecting, Analyzing, and Presenting Usability Metrics" (2nd Edition)}, Elsevier, 2013 
\bibitem{ASQ} J. R. Lewis: \textit{"IBM computer usablity satisfaction questionnaires: Psychometric evaluation and instructions for use"}, International Journal for Human Computer Interactions, 7 (1995), 57-78
\bibitem{EcoVal} M. Brewer: \textit{"Research Design and Issues of Validity"}. In: H. Reis, C. Judd (eds), \textit{"Handbook of Research Methods in Social and Personality Psychology"}, Cambridge University Press, 2000

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{cite}
\usetikzlibrary{positioning}

\author{Bastiaan Weijers \\ 3256669 \and Colin Smits \\ 4075390}
\title{Evaluation of a Body Photo Browser\footnote{Word Count:2957}}
\renewcommand{\familydefault}{\sfdefault}
\begin{document}
\maketitle
\abstract{A computer vision systems recognising gestures in order to operate a photo browser is reviewed. The system evaluation focuses mainly on the accuracy of the system. We see that some gestures are confused, limiting the system's overall performance. The user evaluation is carried out by usability questionnaires. An overall evaluation is given using the PSSUQ, which shows that the system does not meet the standards set for a computer vision system. Parts of the system are evaluated using ASQ and SEQ, which show difference between tasks within the system. Linking both, we see that the way the system is running short of recognising gestures influences the user's perception of the system. }

@@

\subsection{Methods and Environment}
To quantify the performance of the Body Motion program, we setup a test environment to measure how well the system can translate user interaction to concrete system actions. The test setup is contained in an ecologically sound environment, in this case a bedroom with closed curtains was used with as a primary light source three led bulbs lighting the room. There was a single participant used to create quantifying data, whereas the particular user was well introduced to the workings, capabilities and limitations of the system. An analysis of how the system performs when used by lesser informed participants can be found later on in Section 3 - User Evaluation.
\\ The software was used with a YCrCb spectrum at [180 - 210] and a minimum delay of $70ms$ between actions, further settings were left at program-default.
\\ For each action performed in the video recording, a chart was updated with the value the system interpreted it to be. Possible predicted and actual actions were: Next, Previous, CW rotation, CCW rotation and Nothing. Whereas "Nothing" is represented as an idle action wherein nothing happens. It is worth noting that this particular action can only be actively observed on the actual outputs of the system, as predicting idle actions is not possible in our system.
\subsection{Results}
To achieve accurate and representing results, we have recorded a total of 159 actions that we will measure its interpretation by system off, this accounts to roughly 40 actions per possible move.  The number was picked as such because a $n > 30$ will give us a normal distribution over our data [ref needed]. All actions are recorded in a total of two video's, this allows the system to run in a continuous mode, without having to reinitialize after every action. This continuous mode should yield results that are more ecologically sound as opposed to having system global variables reinitialized with every action.
\\ The evaluated output of a the actions will be tested against their expected outputs, the result of this can be found in Table~\ref{table:systemeval}. The data from the table shows the Predicted actions against the Actual actions delivered by the system for every possible action. From the table one can read how many predictions actually translated to correct behavior of the system, and how many did something unexpected.
\\ Table~\ref{table:systemeval} can be parsed to a so-called Confusion Matrix, which is depicted in Table~\ref{table:confusionmatrix}. This matrix is a further generalization and will help us in the question on how well our system performs. Stated before (????, dit is wel in de presentatie gezegd maar nemen we 't op in de paper?), a preferred bias exists in having low false positives as this might be experienced by end-users as undesired behavior. From looking at the Confusion matrix we strongly suspect that we have satisfied this condition, but to confirm this we need to look at the Precision and Recall and establish a PR-curve.
\\ hier een stuk over precision, recall en pr-curve.
\\ moeten we nog een H0 opstellen voor de confusion matrix? We kunnen misschien proeven dat false positive < false negative?
\\ Verder zien we uit Tabel 1 al dat de PR-curve voor swift-left/right er heel anders uit zal zien dan de PR-curve voor rotation. Die laatste is gewoon beroerd, terwijl de precision en recall voor left/right vrij goed zullen zijn. Dit apart testen denk ik in een subhypothese?

@@

\subsection{Methods and Environment}
\label{sub:userMeth}
In our user evaluation, we want to see whether our system is intuitive and easy to use. In order to do that, we need to have a number of people testing our system. First of all, we need to define the environment in which we will be testing. Using the notion of ecological validity, which states that the surroundings in which the research takes place must resemble a real-world setting\cite{brewer2000research}, the tests will take place in normal rooms in terms of for example lighting and background. A laboratory would not be suitable as the user will react differently. The tests are then carried out as follows.

@@

Secondly, in order to get measurements, we set up a questionnaire. According to Sauro and Lewis \cite{sauro2012quantifying}, and Tullis and Albert \cite{albert2013measuring}, there are different standardized questionnaires. For our system, we want to know whether the user is satisfied with the system as a whole. As defined by Sauro and Lewis, the PSSUQ (Post-study System Usability Questionnaire) is "designed to access users' perceived satisfaction with computer system applications" \cite{sauro2012quantifying}. Looking at our goal, we think this questionnaire fits our research. Therefore, we incorporated this questionnaire at the end of the test, after all the scenarios have been completed. We chose the PSSUQ over the SUS (System Usablity Scale), which can also be used as a measure of the usability of a system, due to an increased reliability \cite{sauro2012quantifying}.

In addition, we thought that the user should be able to tell us what he perceived during each scenario. For that, we set up a combination of the ASQ (After Scenario Questionnaire) and the SEQ (Single Ease Question). The AQS was developed by Lewis in order to describe the user's satisfaction with completing a certain task \cite{sauro2012quantifying}\cite{lewis1995ibm}. This can be perfectly used for our research goal. Moreover, the ASQ is linked to the PSSUQ, and also describes the user's satisfaction with a system, in this case a certain task. Furthermore, as the name suggests, the SEQ is used to describe a user's view on the ease of completing a task. The combination is used to get more reliable results.

@@

From the PSSUQ, we can conclude that the system's performance is not good enough, when compared to the PSSUQ norms \cite{sauro2012quantifying}.

@@

\bibliography{mybib}{}
\bibliographystyle{plain}
